Title here

### 2020-07-31 analysis/paper/paper.Rmd
Adds dependencies

pp_regr_season %>% 
  filter_sa() %>% 
  .[, lon := ConvertLongitude(lon)] %>% 
  ggplot(aes(lon, lat)) +
  # geom_raster(aes(fill = estimate)) +
  geom_contour_fill(aes(z = estimate), na.fill = 0, breaks = AnchorBreaks(0, 0.25, 0)) +
  geom_contour2(aes(z = p.value), breaks = 0.01) +
  geom_contour_fill(aes(z = as.numeric(is.na(estimate))), breaks = 1) +
  stat_subset(aes(subset = p.value <= 0.01 & is.cross(lon, lat)), size = 0.4, alpha = 0.3) +
  geom_qmap(~filter_sa(.x)[, lon := ConvertLongitude(lon)], keep = 0.02) +
  scale_x_longitude() +
  scale_y_latitude() +
  scale_fill_divergent("Precipitation", guide = guide_colorstrip_bottom(), 
                       breaks = AnchorBreaks(0, 0.25, 0)) +
  # coord_polar() +
  ggalt::coord_proj("+proj=moll +lon_0=-60") +
  facet_grid(season~term, labeller = labeller(term = lab_sam)) +
  tag_facets() +
  axis_labs_smol 
```

>>>>

pp_regr_season %>% 
  filter_sa() %>% 
  .[, lon := ConvertLongitude(lon)] %>% 
  ggplot(aes(lon, lat)) +
  # geom_raster(aes(fill = estimate)) +
  geom_contour_fill(aes(z = estimate), na.fill = 0, breaks = AnchorBreaks(0, 0.25, 0)) +
  geom_contour2(aes(z = p.value), breaks = 0.01) +
  geom_contour_fill(aes(z = as.numeric(is.na(estimate))), breaks = 1) +
  stat_subset(aes(subset = p.value <= 0.01 & is.cross(lon, lat)), size = 0.4, alpha = 0.3) +
  geom_qmap(~filter_sa(.x)[, lon := ConvertLongitude(lon)], keep = 0.02) +
  scale_x_longitude() +
  scale_y_latitude() +
  scale_fill_divergent("Precipitation", guide = guide_colorstrip_bottom(), 
                       breaks = AnchorBreaks(0, 0.25, 0)) +
  # coord_polar() +
  # ggalt::coord_proj("+proj=moll +lon_0=-60") +
  facet_grid(season~term, labeller = labeller(term = lab_sam)) +
  tag_facets() +
  axis_labs_smol 
```
